---
title: "NC Hotel Group: Late Cancellation Analysis"
subtitle: "Where are late cancellations concentrated, and what evidence can guide a targeted response?"
format:
  html:
    toc: true
    toc-depth: 2
    number-sections: true
    code-fold: false
    code-tools: true
    embed-resources: true
    theme: cosmo
execute:
  echo: true
  warning: false
  message: false
  error: false
  cache: false
fig-width: 10
fig-height: 6
---

## What data and definitions will we use?

One row represents one booking. **Late cancellation** means `status == "Canceled"` with 0-7 days of notice, including arrival day. No-shows remain a separate outcome. Booking value is booked nights x average daily rate, not verified revenue loss.

```{r}
#| label: setup
library(tidyverse)
library(lubridate)

nc_hotel_raw <- read_csv("nc_hotel_group.csv", show_col_types = FALSE)

# Stop if the input no longer contains the variables needed below.
required_columns <- c(
  "property", "status", "canceled", "status_date", "arrival_year",
  "arrival_month", "arrival_day_of_month", "booking_channel",
  "weekend_stays", "week_stays", "average_daily_rate", "deposit_terms",
  "advance_time", "num_adults", "num_children"
)
stopifnot(all(required_columns %in% names(nc_hotel_raw)))

# Display full tables with rounded numbers; calculations retain full precision.
show_table <- function(data, caption = NULL, digits = 2) {
  knitr::kable(data, caption = caption, digits = digits)
}

theme_set(theme_minimal(base_size = 12))
theme_update(
  panel.grid.minor = element_blank(),
  plot.title = element_text(face = "bold"),
  plot.caption = element_text(hjust = 0),
  legend.position = "bottom"
)
accent <- "#C46532"
neutral <- "#526779"

tibble(
  bookings = nrow(nc_hotel_raw),
  variables = ncol(nc_hotel_raw)
) |> show_table()

# Inspect structure without printing individual booking records in full.
glimpse(nc_hotel_raw)
```

## How are booking outcomes coded?

```{r}
#| label: booking-outcomes
outcome_summary <- nc_hotel_raw |>
  count(status, canceled, name = "bookings") |>
  mutate(share_pct = 100 * bookings / sum(bookings))

outcome_summary |> show_table()

# The binary flag includes no-shows; use status for actual cancellations.
stopifnot(all(
  nc_hotel_raw$canceled ==
    as.integer(nc_hotel_raw$status %in% c("Canceled", "No-Show"))
))

nc_hotel_raw |>
  filter(status == "Canceled") |>
  select(status, status_date) |>
  slice_head(n = 6) |>
  show_table(caption = "Example cancellation dates before conversion")
```

## How far before arrival do cancellations occur?

`status_date` is used as the cancellation date only for canceled bookings. Booking lead time (`advance_time`) is a different measure: booking to arrival.

```{r}
#| label: derive-analysis-variables
# Derive variables once so every later subset uses the same definitions.
nc_hotel <- nc_hotel_raw |>
  mutate(
    status_date = ymd(status_date),
    arrival_date = make_date(
      arrival_year, match(arrival_month, month.name), arrival_day_of_month
    ),
    actual_cancellation = status == "Canceled",
    days_before_arrival = if_else(
      actual_cancellation,
      as.numeric(arrival_date - status_date),
      NA_real_
    ),
    total_nights = weekend_stays + week_stays,
    booking_value = total_nights * average_daily_rate,
    zero_recorded_guests = num_adults == 0 & num_children == 0
  )

cancellations <- nc_hotel |> filter(actual_cancellation)

cancellations |>
  select(arrival_date, status_date, days_before_arrival) |>
  slice_head(n = 6) |>
  show_table()

notice_audit <- cancellations |>
  summarise(
    cancellations = n(),
    missing_notice = sum(is.na(days_before_arrival)),
    negative_notice = sum(days_before_arrival < 0, na.rm = TRUE),
    same_day = sum(days_before_arrival == 0, na.rm = TRUE),
    notice_exceeds_booking_lead = sum(
      days_before_arrival > advance_time, na.rm = TRUE
    )
  )
notice_audit |> show_table()

cancellations |>
  filter(is.na(days_before_arrival) | days_before_arrival < 0) |>
  select(property, arrival_date, status_date, days_before_arrival) |>
  show_table(caption = "Missing or negative cancellation notice: records requiring review")

summary(cancellations$days_before_arrival)

# All-cancellation denominators below require known, nonnegative notice.
# Fail visibly if a future input would silently classify unknown timing as early.
stopifnot(
  notice_audit$missing_notice == 0,
  notice_audit$negative_notice == 0
)

is_late <- function(status, notice, window = 7) {
  status == "Canceled" & !is.na(notice) & between(notice, 0, window)
}
nc_hotel <- nc_hotel |>
  mutate(late_cancellation = is_late(status, days_before_arrival))
cancellations <- nc_hotel |> filter(actual_cancellation)

notice_distribution <- cancellations |>
  mutate(notice_group = cut(
    days_before_arrival,
    breaks = c(-Inf, 0, 3, 7, 14, 30, 90, Inf),
    labels = c("Arrival day", "1-3 days", "4-7 days", "8-14 days",
               "15-30 days", "31-90 days", "91+ days")
  )) |>
  count(notice_group, .drop = FALSE, name = "cancellations") |>
  mutate(share_pct = 100 * cancellations / sum(cancellations))
notice_distribution |> show_table()

overall_summary <- nc_hotel |>
  summarise(
    all_bookings = n(),
    cancellations = sum(actual_cancellation),
    late_cancellations = sum(late_cancellation),
    late_share_of_cancellations_pct = 100 * late_cancellations / cancellations,
    late_rate_all_bookings_pct = 100 * late_cancellations / all_bookings
  )
overall_summary |> show_table()
```

## Are stay lengths, rates, guest counts, and categories usable?

All recorded bookings remain in the main frequency analysis. Value, deposit, and lead-time analyses use overnight bookings (`total_nights > 0`); zero rates are retained. Records with no adults or children recorded are flagged and checked separately.

```{r}
#| label: data-quality
nc_hotel_raw |>
  summarise(across(everything(), ~ sum(is.na(.x)))) |>
  pivot_longer(everything(), names_to = "variable", values_to = "missing") |>
  show_table(caption = "Missing values in the original data")

quality_summary <- nc_hotel |>
  summarise(
    zero_nights = sum(total_nights == 0, na.rm = TRUE),
    missing_nights = sum(is.na(total_nights)),
    negative_stay_components = sum(weekend_stays < 0 | week_stays < 0, na.rm = TRUE),
    zero_rates = sum(average_daily_rate == 0, na.rm = TRUE),
    negative_rates = sum(average_daily_rate < 0, na.rm = TRUE),
    missing_rates = sum(is.na(average_daily_rate)),
    zero_recorded_guests = sum(zero_recorded_guests, na.rm = TRUE),
    missing_guest_counts = sum(is.na(num_adults) | is.na(num_children)),
    negative_guest_counts = sum(num_adults < 0 | num_children < 0, na.rm = TRUE),
    missing_lead_time = sum(is.na(advance_time)),
    negative_lead_time = sum(advance_time < 0, na.rm = TRUE)
  )
quality_summary |>
  pivot_longer(everything(), names_to = "check", values_to = "bookings") |>
  show_table()

nc_hotel |>
  select(total_nights, average_daily_rate, num_adults, num_children, advance_time) |>
  summary()

nc_hotel |>
  filter(total_nights == 0) |>
  count(property, status) |>
  show_table(caption = "Zero-night bookings")

nc_hotel |>
  filter(zero_recorded_guests) |>
  count(property, status) |>
  show_table(caption = "Bookings with no adults or children recorded")

nc_hotel |>
  arrange(desc(average_daily_rate)) |>
  select(property, status, total_nights, average_daily_rate) |>
  slice_head(n = 6) |>
  show_table(caption = "Highest daily rates: inspect, do not automatically delete")

nc_hotel |>
  arrange(desc(num_adults)) |>
  select(property, booking_channel, num_adults, num_children,
         total_nights, average_daily_rate, status) |>
  slice_head(n = 6) |>
  show_table(caption = "Largest recorded adult counts")

nc_hotel |>
  select(property, status, booking_channel, deposit_terms) |>
  pivot_longer(everything(), names_to = "variable", values_to = "category") |>
  mutate(needs_review = is.na(category) |
           str_to_lower(str_trim(category)) %in% c("", "undefined", "unknown")) |>
  count(variable, category, needs_review) |>
  show_table(caption = "Category coverage and missing or undefined labels")

# Protect booking-value totals from silently dropping missing/negative inputs.
stopifnot(
  quality_summary$missing_nights == 0,
  quality_summary$negative_stay_components == 0,
  quality_summary$missing_rates == 0,
  quality_summary$negative_rates == 0
)
```

## Does late-cancellation frequency differ by property?

The late share among cancellations and the late rate among all bookings answer different questions. All-booking denominators include no-shows and zero-night records.

```{r}
#| label: property-comparison
property_summary <- nc_hotel |>
  group_by(property) |>
  summarise(
    all_bookings = n(),
    cancellations = sum(actual_cancellation),
    late_cancellations = sum(late_cancellation),
    .groups = "drop"
  ) |>
  mutate(
    cancellation_rate_pct = 100 * cancellations / all_bookings,
    late_share_of_cancellations_pct = 100 * late_cancellations / cancellations,
    late_rate_all_bookings_pct = 100 * late_cancellations / all_bookings
  )
property_summary |> show_table()
```

```{r}
#| label: fig-property-rates
#| fig-cap: "Late cancellations as a percentage of all recorded bookings at each property."
property_rate_plot <- property_summary |>
  mutate(label = sprintf(
    "%.2f%%\n%s of %s bookings", late_rate_all_bookings_pct,
    scales::comma(late_cancellations), scales::comma(all_bookings)
  )) |>
  ggplot(aes(property, late_rate_all_bookings_pct, fill = property)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.35, size = 4) +
  scale_fill_manual(values = c("City Hotel" = accent, "Resort Hotel" = neutral)) +
  scale_y_continuous(labels = scales::label_number(suffix = "%"),
                     expand = expansion(mult = c(0, 0.3))) +
  labs(title = "Late-cancellation rates by property", x = NULL,
       y = "Late cancellations / all bookings",
       caption = "Late = canceled 0-7 days before arrival. No-shows excluded from numerator.")
property_rate_plot
```

## Which property and channel combinations contribute the most late cancellations?

```{r}
#| label: channel-frequency
channel_summary <- nc_hotel |>
  group_by(property, booking_channel) |>
  summarise(
    all_bookings = n(),
    cancellations = sum(actual_cancellation),
    late_cancellations = sum(late_cancellation),
    .groups = "drop"
  ) |>
  mutate(
    late_rate_pct = 100 * late_cancellations / all_bookings,
    share_of_all_late_pct = 100 * late_cancellations / sum(late_cancellations)
  ) |>
  arrange(desc(late_cancellations))

# Counts show scale; rates use each channel's own booking denominator.
channel_summary |> show_table()
```

## Where is late-canceled booking value concentrated?

These totals exclude zero-night stays. They do not account for deposits collected, cancellation fees, room resale, or operating costs. Values use the daily-rate units in the source data.

```{r}
#| label: booking-value
overnight_bookings <- nc_hotel |> filter(total_nights > 0)
late_cancellation_values <- overnight_bookings |> filter(late_cancellation)

nc_hotel |>
  summarise(
    all_bookings = n(),
    overnight_bookings = sum(total_nights > 0),
    all_late_cancellations = sum(late_cancellation),
    zero_night_late_cancellations = sum(late_cancellation & total_nights == 0),
    overnight_late_cancellations = sum(late_cancellation & total_nights > 0)
  ) |>
  show_table(caption = "Reconcile all-booking and overnight-only populations")

channel_value_summary <- late_cancellation_values |>
  group_by(property, booking_channel) |>
  summarise(
    late_cancellations = n(),
    booked_nights = sum(total_nights),
    summed_booking_value = sum(booking_value),
    mean_booking_value = mean(booking_value),
    median_booking_value = median(booking_value),
    .groups = "drop"
  ) |>
  mutate(value_share_pct = 100 * summed_booking_value / sum(summed_booking_value)) |>
  arrange(desc(summed_booking_value))
channel_value_summary |> show_table()

late_cancellation_values |>
  filter(zero_recorded_guests) |>
  select(property, booking_channel, num_adults, num_children,
         days_before_arrival, total_nights, booking_value) |>
  show_table(caption = "Late-canceled overnight bookings with no recorded guests")
```

```{r}
#| label: fig-channel-value
#| fig-height: 7
#| fig-cap: "Booked lodging value attached to late cancellations, by property and channel."
channel_value_plot <- channel_value_summary |>
  mutate(
    channel_label = paste(property, booking_channel, sep = " | "),
    highlight = property == "City Hotel" & booking_channel == "Online TA"
  ) |>
  ggplot(aes(summed_booking_value, reorder(channel_label, summed_booking_value),
             fill = highlight)) +
  geom_col(width = 0.7) +
  geom_text(aes(label = scales::comma(summed_booking_value, accuracy = 1)),
            hjust = -0.15, size = 3.5) +
  scale_fill_manual(values = c("FALSE" = neutral, "TRUE" = accent), guide = "none") +
  scale_x_continuous(labels = scales::label_comma(),
                     expand = expansion(mult = c(0, 0.25))) +
  labs(title = "Late-canceled booking value by property and channel",
       subtitle = "Overnight bookings canceled 0-7 days before arrival",
       x = "Booked lodging value (source daily-rate units)", y = NULL,
       caption = "Nights x average daily rate; not verified revenue loss. Deposits and room resale unobserved.")
channel_value_plot
```

## What do deposit terms tell us about City Hotel Online TA bookings?

Both the numerator and denominator below use overnight bookings in this segment. Deposit terms describe the reservation, not proof of payment; small deposit groups cannot establish deposit effectiveness.

```{r}
#| label: deposit-comparison
city_online_bookings <- overnight_bookings |>
  filter(property == "City Hotel", booking_channel == "Online TA")

city_online_bookings |>
  filter(late_cancellation) |>
  group_by(deposit_terms) |>
  summarise(
    late_cancellations = n(),
    summed_booking_value = sum(booking_value),
    .groups = "drop"
  ) |>
  show_table(caption = "Deposit terms among late cancellations")

deposit_comparison <- city_online_bookings |>
  group_by(deposit_terms) |>
  summarise(
    all_bookings = n(),
    late_cancellations = sum(late_cancellation),
    .groups = "drop"
  ) |>
  mutate(late_rate_pct = 100 * late_cancellations / all_bookings)
deposit_comparison |> show_table(caption = "Late-cancellation rate within each deposit category")
```

## Does booking lead time distinguish cancellation patterns in this segment?

Rates use all overnight bookings within each lead-time group. Late cancellations are a subset of all cancellations; short-lead bookings have less opportunity to cancel early.

```{r}
#| label: lead-time-comparison
summary(city_online_bookings$advance_time)

city_online_bookings <- city_online_bookings |>
  mutate(
    lead_time_group = case_when(
      is.na(advance_time) ~ "Missing",
      advance_time < 0 ~ "Invalid",
      advance_time <= 7 ~ "0-7 days",
      advance_time <= 30 ~ "8-30 days",
      advance_time <= 90 ~ "31-90 days",
      TRUE ~ "91+ days"
    ),
    lead_time_group = factor(lead_time_group, levels = c(
      "0-7 days", "8-30 days", "31-90 days", "91+ days", "Missing", "Invalid"
    ))
  )

lead_time_summary <- city_online_bookings |>
  group_by(lead_time_group) |>
  summarise(
    all_bookings = n(),
    cancellations = sum(actual_cancellation),
    late_3_days = sum(is_late(status, days_before_arrival, 3)),
    late_7_days = sum(late_cancellation),
    late_14_days = sum(is_late(status, days_before_arrival, 14)),
    .groups = "drop"
  ) |>
  mutate(
    cancellation_rate_pct = 100 * cancellations / all_bookings,
    late_3_days_rate = 100 * late_3_days / all_bookings,
    late_7_days_rate = 100 * late_7_days / all_bookings,
    late_14_days_rate = 100 * late_14_days / all_bookings
  )
lead_time_summary |> show_table()
```

```{r}
#| label: fig-lead-time
#| fig-cap: "All-cancellation and late-cancellation rates within City Hotel Online TA lead-time groups."
lead_time_plot_data <- lead_time_summary |>
  select(lead_time_group, cancellation_rate_pct, late_7_days_rate) |>
  pivot_longer(-lead_time_group, names_to = "measure", values_to = "rate") |>
  mutate(measure = recode(measure,
    cancellation_rate_pct = "All cancellations",
    late_7_days_rate = "Late cancellations (0-7 days)"
  ))

lead_time_plot <- ggplot(lead_time_plot_data,
                         aes(lead_time_group, rate, fill = measure)) +
  geom_col(position = position_dodge(0.8), width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", rate)),
            position = position_dodge(0.8), vjust = -0.4, size = 3.5) +
  scale_fill_manual(values = c("All cancellations" = neutral,
                               "Late cancellations (0-7 days)" = accent)) +
  scale_y_continuous(labels = scales::label_number(suffix = "%"),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Cancellation patterns by booking lead time",
       subtitle = "City Hotel | Online TA | Overnight bookings",
       x = "Booking lead time", y = "Percentage of bookings in each group", fill = NULL,
       caption = "No-shows excluded from both numerators. Late cancellations are a subset of all cancellations.")
lead_time_plot
```

## Do the findings depend on the late window or inclusion rules?

Each window includes arrival day and uses a fixed denominator. The guest-count check removes flagged bookings from both numerator and denominator.

```{r}
#| label: window-sensitivity
# Recheck property rates and channel value rankings, not just lead-time groups.
window_data <- map_dfr(c(3, 7, 14), function(window) {
  nc_hotel |>
    mutate(window_days = window,
           late_in_window = is_late(status, days_before_arrival, window))
})

property_window_summary <- window_data |>
  group_by(window_days, property) |>
  summarise(all_bookings = n(), late_cancellations = sum(late_in_window),
            .groups = "drop") |>
  mutate(late_rate_pct = 100 * late_cancellations / all_bookings)
property_window_summary |> show_table()

channel_window_summary <- window_data |>
  filter(total_nights > 0, late_in_window) |>
  group_by(window_days, property, booking_channel) |>
  summarise(late_cancellations = n(), summed_booking_value = sum(booking_value),
            .groups = "drop") |>
  group_by(window_days) |>
  mutate(value_rank = min_rank(desc(summed_booking_value))) |>
  ungroup()
channel_window_summary |>
  filter(value_rank <= 3) |>
  arrange(window_days, value_rank) |>
  show_table(caption = "Top three property/channel groups by booking value under each window")
```

```{r}
#| label: fig-window-sensitivity
#| fig-width: 12
#| fig-cap: "Late-cancellation rates under 3-, 7-, and 14-day definitions, with fixed lead-time group denominators."
sensitivity_plot_data <- lead_time_summary |>
  select(lead_time_group, late_3_days_rate, late_7_days_rate, late_14_days_rate) |>
  pivot_longer(-lead_time_group, names_to = "window", values_to = "rate") |>
  mutate(
    window = factor(window,
      levels = c("late_3_days_rate", "late_7_days_rate", "late_14_days_rate"),
      labels = c("Within 3 days", "Within 7 days", "Within 14 days")),
    shorter_lead = lead_time_group %in% c("0-7 days", "8-30 days")
  )

group_size_caption <- paste(
  paste(lead_time_summary$lead_time_group,
        scales::comma(lead_time_summary$all_bookings), sep = ": n = "),
  collapse = "; "
)

sensitivity_plot <- ggplot(sensitivity_plot_data,
                            aes(lead_time_group, rate, fill = shorter_lead)) +
  geom_col(width = 0.7, show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.1f%%", rate)), vjust = -0.4, size = 3.3) +
  facet_wrap(~ window, nrow = 1) +
  scale_fill_manual(values = c("TRUE" = accent, "FALSE" = neutral)) +
  scale_y_continuous(labels = scales::label_number(suffix = "%"),
                     expand = expansion(mult = c(0, 0.2))) +
  labs(title = "Does the late-cancellation pattern change with the window?",
       subtitle = "City Hotel | Online TA | Overnight bookings",
       x = "Booking lead time", y = "Late cancellations / bookings in each group",
       caption = paste(group_size_caption,
         "Shorter-lead bookings have less opportunity to cancel early; comparisons are descriptive.",
         sep = "\n")) +
  theme(axis.text.x = element_text(size = 9))
sensitivity_plot
```

```{r}
#| label: inclusion-sensitivity
inclusion_data <- bind_rows(
  nc_hotel |> mutate(population = "All recorded bookings"),
  overnight_bookings |> mutate(population = "Overnight bookings"),
  overnight_bookings |>
    filter(!is.na(zero_recorded_guests), !zero_recorded_guests) |>
    mutate(population = "Overnight, recorded guests > 0")
)

inclusion_data |>
  group_by(population, property) |>
  summarise(
    all_bookings = n(),
    late_cancellations = sum(late_cancellation),
    late_rate_pct = 100 * late_cancellations / all_bookings,
    .groups = "drop"
  ) |>
  show_table(caption = "Property rates under different inclusion rules")

inclusion_data |>
  filter(total_nights > 0, late_cancellation) |>
  group_by(population, property, booking_channel) |>
  summarise(summed_booking_value = sum(booking_value), .groups = "drop") |>
  group_by(population) |>
  slice_max(summed_booking_value, n = 1, with_ties = TRUE) |>
  ungroup() |>
  show_table(caption = "Highest-value segment under each inclusion rule")

inclusion_data |>
  filter(property == "City Hotel", booking_channel == "Online TA") |>
  group_by(population) |>
  summarise(
    all_bookings = n(),
    late_cancellations = sum(late_cancellation),
    late_rate_pct = 100 * late_cancellations / all_bookings,
    late_booking_value = sum(booking_value[late_cancellation]),
    .groups = "drop"
  ) |>
  show_table(caption = "Effect of inclusion rules on the selected segment")
```

## What evidence should guide the presentation and next action?

```{r}
#| label: evidence-summary
priority_segment <- channel_value_summary |> slice_max(summed_booking_value, n = 1)

tibble(
  question = c(
    "How common are late cancellations?",
    "Which property has the higher all-booking late rate?",
    "Which segment has the most late-canceled booking value?"
  ),
  answer = c(
    sprintf("%s of %s bookings (%.2f%%); %.2f%% of cancellations",
      scales::comma(overall_summary$late_cancellations),
      scales::comma(overall_summary$all_bookings),
      overall_summary$late_rate_all_bookings_pct,
      overall_summary$late_share_of_cancellations_pct),
    property_summary |>
      slice_max(late_rate_all_bookings_pct, n = 1, with_ties = FALSE) |>
      transmute(answer = sprintf("%s: %.2f%%", property, late_rate_all_bookings_pct)) |>
      pull(answer),
    sprintf("%s | %s: %s (%.1f%% of total late booking value)",
      priority_segment$property, priority_segment$booking_channel,
      scales::comma(priority_segment$summed_booking_value, accuracy = 0.01),
      priority_segment$value_share_pct)
  )
) |> show_table()
```

Prioritize a measured follow-up in the highest-value segment and test pre-arrival communication, using the lead-time results to plan the pilot. These descriptive results do not establish a causal effect of deposits or lead time, actual revenue loss, or a safe overbooking number.

## How can the results be reproduced and reused in slides?

Render this file from the project folder with `quarto render Report.qmd`. The code below saves the four charts and key tables for a separate presentation.

```{r}
#| label: export-results
dir.create("figures", showWarnings = FALSE)
dir.create("analysis_tables", showWarnings = FALSE)

ggsave("figures/01_property_late_rates.png", property_rate_plot,
       width = 11, height = 6.5, dpi = 300, bg = "white")
ggsave("figures/02_channel_booking_value.png", channel_value_plot,
       width = 12, height = 8, dpi = 300, bg = "white")
ggsave("figures/03_lead_time_rates.png", lead_time_plot,
       width = 12, height = 7, dpi = 300, bg = "white")
ggsave("figures/04_window_sensitivity.png", sensitivity_plot,
       width = 13, height = 7, dpi = 300, bg = "white")

write_csv(property_summary, "analysis_tables/property_summary.csv")
write_csv(channel_summary, "analysis_tables/channel_frequency.csv")
write_csv(channel_value_summary, "analysis_tables/channel_booking_value.csv")
write_csv(deposit_comparison, "analysis_tables/deposit_comparison.csv")
write_csv(lead_time_summary, "analysis_tables/lead_time_summary.csv")
write_csv(property_window_summary, "analysis_tables/property_window_sensitivity.csv")
write_csv(channel_window_summary, "analysis_tables/channel_window_sensitivity.csv")

# Reconciliation checks tie every subgroup back to its source population.
stopifnot(
  sum(property_summary$all_bookings) == nrow(nc_hotel),
  sum(channel_summary$late_cancellations) == sum(nc_hotel$late_cancellation),
  sum(channel_value_summary$late_cancellations) == nrow(late_cancellation_values),
  sum(deposit_comparison$all_bookings) == nrow(city_online_bookings),
  sum(lead_time_summary$all_bookings) == nrow(city_online_bookings),
  all(lead_time_summary$late_3_days <= lead_time_summary$late_7_days),
  all(lead_time_summary$late_7_days <= lead_time_summary$late_14_days),
  all(lead_time_summary$late_14_days <= lead_time_summary$cancellations)
)
```

```{r}
#| label: session-information
#| code-fold: true
sessionInfo()
```
